PID Controller Implementation in CARLA Simulator

### 2024-12-02 Article.tex
Update Article.tex

This research aims to enable a vehicle to accurately follow a predefined route and maintain the desired speed while ensuring stability and minimizing collision risks, thereby enhancing knowledge in cyber-physical systems and PID control. The core components of this project include:

@@

\subsection{Route Management and Waypoint Planning}
The route is defined through a series of waypoints ($w_i$) extracted from an XML file or generated through camera-based waypoint tracing. The waypoints are represented as 3D positions in the form:

@@

\subsubsection{Throttle Control}
The target speed $v_{\text{target}}$ is compared with the current speed $v_{\text{current}}$ to calculate the speed error ($e_v = v_{\text{target}} - v_{\text{current}}$). The PID control action for the throttle is computed as:

@@

Ten user-defined routes were created using CARLA's camera as a route planner with varying complexities (eg. varying numbers of turns), and all routes were successfully completed. An example of a simulation with the route can be seen in Figure~\ref{fig:route}

@@

For route tracking, a lookahead of three waypoints was set after trial and error. Using a single waypoint resulted in collisions in some scenarios while analyzing the entire path at every time point without a lookahead also led to collisions. Although an unwanted state happened in these scenarios they were useful to prove Hypothesis 3, where the simulation ended and the next started as soon as the collision happened.

@@

Regarding speed maintenance, the PID controller was appropriately fine-tuned. Most of the time, the vehicle stayed outside the target speed during the initial acceleration period when the simulation started, and the car smoothly accelerated to reach the target speed.

@@

Future work could involve exploring more advanced control strategies or adaptive PID tuning to enhance performance in complex driving scenarios. Additionally, varying the vehicle's speed, adding turns that are not 90 degrees, experimenting with different simulation environments, and integrating computer vision techniques could lead to a fully autonomous vehicle without the need for manual route planning.

@@

ChatGPT and GitHub Copilot were used to develop and polish the code and text.

>>>>

This research aims to enable a vehicle to accurately follow a predefined route and maintain desired speed while ensuring stability and minimizing collision risks, thereby enhancing knowledge in cyber-physical systems and PID control. The core components of this project include:

@@

\subsection{Route Management and Waypoint Planning}
The route is defined through a series of waypoints ($w_i$) extracted from an XML file or generated through the camera-based waypoint tracing. The waypoints are represented as 3D positions in the form:

@@

\subsubsection{Throttle Control}
The target speed $v_{\text{target}}$ is compared with the current speed $v_{\text{current}}$ to calculate the speed error ($e_v = v_{\text{target}} - v_{\text{current}}$). The PID control action for throttle is computed as:

@@

Ten user-defined routes were created using CARLA's camera as a route planner, and all routes were successfully completed. An example of a simulation with the route can be seen in Figure~\ref{fig:route}

@@

For route tracking, a lookahead of three waypoints was set after trial and error. Using a single waypoint resulted in collisions in some scenarios, while analyzing the entire path at every time point without lookahead also led to collisions.

@@

Regarding speed maintenance, the PID controller was appropriately fine-tuned. Most of the time the vehicle stayed outside the target speed was during the initial acceleration period when the simulation started, and the car was smoothly accelerating to reach the target speed.

@@

Future work could involve exploring more advanced control strategies or adaptive PID tuning to enhance performance in complex driving scenarios. Additionally, varying the vehicle's speed, experimenting with different simulation environments, and integrating computer vision techniques could lead to a fully autonomous vehicle without the need for manual route planning.

@@

ChatGPT and GitHub Copilot were used in the development and polishing of the code and text.
